DOM review: Data preparation

### 2023-01-24 Analysis/Code/1_DataPrep.Rmd
working on survey page of spreadsheet

## Species and Location
This sheet describes the study species and area. Some papers with multi-species models may have multiple entries.
```{r Process Species/Location, echo = FALSE}
taxa_location_sheet <- spreadsheet[["Species and Location"]] %>%
  # Filter to included papers
  filter(Status == "Complete") %>%
  # Create binary threat columns
  mutate(Threat_HabitatLoss = str_detect(`Threat categories`, "HabitatLoss"),
         Threat_Exploitation = str_detect(`Threat categories`, "Exploitation"),
         Threat_ClimateChange = str_detect(`Threat categories`, "ClimateChange"),
         Threat_Invasives = str_detect(`Threat categories`, "Invasives"),
         Threat_Disease = str_detect(`Threat categories`, "Disease"),
         Threat_Disaster = str_detect(`Threat categories`, "Disturbance")) %>%
  # Select only necessary files
  select(`Review ID`, Title, Taxa, `Taxa keywords`, Number, 
         Threat_HabitatLoss, Threat_Exploitation, Threat_ClimateChange,
         Threat_Invasives, Threat_Disease, Threat_Disaster,
         Country, Continent, Realm, `Study Size`)
```

This section includes several fields which require checks
```{r Check Species/Location, echo = FALSE}

>>>>

## Species and Location
This sheet describes the study species and area. Some papers with multi-species models may have multiple entries.
```{r Process Species/Location, echo = FALSE}
taxa_location_sheet <- spreadsheet[["Species and Location"]] %>%
  # Filter to included papers
  filter(Status == "Complete") %>%
  # Create binary threat columns
  mutate(Threat_HabitatLoss = str_detect(`Threat categories`, "HabitatLoss"),
         Threat_Exploitation = str_detect(`Threat categories`, "Exploitation"),
         Threat_ClimateChange = str_detect(`Threat categories`, "ClimateChange"),
         Threat_Invasives = str_detect(`Threat categories`, "Invasives"),
         Threat_Disease = str_detect(`Threat categories`, "Disease"),
         Threat_Disaster = str_detect(`Threat categories`, "Disturbance")) %>%
  # Split 'taxa keywords' column by commas
  separate_rows(`Taxa keywords`, sep = ", ") %>%
  # Split country column by commas
  separate_rows(Country, sep = ", ") %>%
  # Select only necessary fields
  select(`Review ID`, Title, Taxa, `Taxa keywords`, Number, 
         Threat_HabitatLoss, Threat_Exploitation, Threat_ClimateChange,
         Threat_Invasives, Threat_Disease, Threat_Disaster,
         Country, Continent, Realm, `Study Size`)
```

This section includes a few fields which require checks
```{r Check Species/Location, echo = FALSE}
# Are all taxa names appropriate?
unique(taxa_location_sheet$Taxa)

# Should any taxa categories be condensed or removed?
unique(taxa_location_sheet$`Taxa keywords`)

# Are all country names correct?
taxa_location_sheet %>% count(Country) %>% arrange(-n)
```

## Data collection
This sheet includes information on survey and sampling techniques
```{r Process Data Collection, echo = FALSE}
survey_sheet <- spreadsheet[["Data collection"]] %>%
  # Filter to included papers
  filter(Status == "Complete") %>% 
  # Split capture method and sampling method fields
  separate_rows(`Capture method`, sep = ", ") %>%
  separate_rows(`Sampling method`, sep = ", ") %>%
  #

  mutate(MinPrimary = `Number of primary occasions`,
         MaxPrimary = `Number of primary occasions`) %>%
  map_dfr(.f = function(.x){
    if (str_detect(.x$MinPrimary, "-")){
      .x$MinPrimary <- str_split(.x$MinPrimary[[1]])
      .x$MaxPrimary <- str_split(.x$MaxPrimary[[2]])
    }
  })

  mutate(MinPrimary = case_when(str_detect(`Number of primary occasions`, "-") ~
                                  str_split(`Number of primary occasions`, "-")[[1]],
                                !str_detect(`Number of primary occasions`, "-") ~
                                  `Number of primary occasions`),
         MaxPrimary = case_when(str_detect(`Number of primary occasions`, "-") ~
                                  str_split(`Number of primary occasions`, "-")[[2]],
                                !str_detect(`Number of primary occasions`, "-") ~
                                  `Number of primary occasions`))

        function(test){}

  # Select important fields
  select(`Review ID`, Title, `Study duration`, `Capture method`, 
         `Num primary` = `Number of primary occasions`,
         `Num secondary` = `Number of secondary occasions`,
         `Type secondary` = `Type of secondary occasions`,
         `Type site` = `Type of site`, `Num sites` = `Number of sites`,
         `Sampling method`)
